```{r init, echo=FALSE}
library("ggplot2")
library("RCurl")
library("plyr")
library("scales")
readRenviron("~/.Renviron") # Make sure you have a APPMETRICS_CREDENTIALS=username:password entry
metrics_credentials <- Sys.getenv(c("APPMETRICS_CREDENTIALS"))
```

```{r fetchData0, echo=FALSE}
application <- "CIAPILatencyCollector" 
startTime <- "2012-09-04 13:00:00"
endTime <- "2012-09-10 23:59:59"
data_url <- URLencode(paste("http://metrics.cityindex.com/GetRecords.ashx?Application=",application,"&StartTime=",startTime,'&EndTime=',endTime, sep = ''))

webpage <- getURL(data_url,userpwd=metrics_credentials, httpauth = 1L)
logdata <- read.table(tc <- textConnection(webpage), header=F, sep="\t", fill=TRUE, as.is=c(1,4)); 
close(tc)
colnames(logdata)=c('session','timestamp','key','value')
```

```{r groupSessionByNodes0, echo=FALSE}
nodes <- logdata[logdata$"key" %in% c("Info_NodeName"), ]

#temp bugfix - this session doesn't seem to report a ClientIP
nodes[3,] <- c("39d948e7-5f2c-4b24-995e-94f1f6c3eab6", "2012-09-03 13:45:42.5018590", "NodeName", "AWS-EU-WEST-1B-79.125.25.36")

nodes$nodeName = nodes$value

nodes <- subset(nodes, select=c(-timestamp,-key,-value))
```

Latency between different endpoints
-----------------------------------
The following chart compares the latency of the Default IIS page from different 
endpoints.  The IIS default page is assumed to be the fasted response the server can give, so this
measures the latency due to the network:
```{r network_latency_plot, fig.width=10, fig.height = 7, tidy=FALSE, warning=FALSE}
rpc <- logdata[logdata$"key" %in% c("Latency General.DefaultPage"), ]
rpc$datetime <- strptime(rpc$timestamp, "%Y-%m-%d %H:%M:%S")
rpc <- join(rpc, nodes, by = "session", match = "first")

d <- ggplot(rpc, aes(x=datetime, y=as.double(value)))
d <- d + scale_y_continuous(limits=c(0.001, 1))
d <- d + geom_hex()
d <- d + stat_quantile( quantiles = c(0.5, 0.98) ) 
d <- d + geom_rug(aes(x=NULL, y=as.double(value)), col=rgb(.5,0,0, alpha=.05))
d <- d + scale_fill_gradient(low="grey", high="red") + theme_bw()
d <- d + facet_grid(nodeName ~ key)
print(d)
```
As is expected, both the latency measures and the variability is higher for nodes geographically further away.

The collection nodes currently have a memory leak issue that causes periodic failure to collect data (hence the gaps.)  This will be addressed in the next release.

```{r fetchData, echo=FALSE}
application <- "CIAPILatencyCollector.AllServiceMonitor.BuiltIn" #will switch to CIAPILatencyCollector once https://github.com/fandrei/AppMetrics/issues/101 has been resolved
startTime <- "2012-09-04 13:00:00"
endTime <- "2012-09-10 23:59:59"
data_url <- URLencode(paste("http://metrics.cityindex.com/GetRecords.ashx?Application=",application,"&StartTime=",startTime,'&EndTime=',endTime, sep = ''))

webpage <- getURL(data_url,userpwd=metrics_credentials, httpauth = 1L)
logdata <- read.table(tc <- textConnection(webpage), header=F, sep="\t", fill=TRUE, as.is=c(1,4)); 
close(tc)
colnames(logdata)=c('session','timestamp','key','value')
```

```{r convert_to_CIAPILatencyCollector_names, echo=FALSE}
# Temporary measure to convert CIAPILatencyCollector.AllServiceMonitor.BuiltIn names to CIAPILatencyCollector names.  Will not be needed once https://github.com/fandrei/AppMetrics/issues/101 has been resolved
logdata$key <- sub('Latency https://ciapi.cityindex.com/TradingApi/', 'Latency CIAPI.',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.session/deleteSession', 'Latency CIAPI.LogOut',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.session', 'Latency CIAPI.LogIn',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.spread/markets?MarketName=&MarketCode=&ClientAccountId=400194351&MaxResults=100&UseMobileShortName=False', 'Latency CIAPI.ListSpreadMarkets',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.useraccount/UserAccount/ClientAndTradingAccount', 'Latency CIAPI.GetClientAndTradingAccount',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.market/400616150/information', 'Latency CIAPI.GetMarketInformation',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.market/400616150/barhistory?interval=MINUTE&span=1&PriceBars=20', 'Latency CIAPI.GetPriceBars',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.order/order/openpositions?TradingAccountId=400290710', 'Latency CIAPI.ListOpenPositions',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.news/dj/UK?MaxResults=10', 'Latency CIAPI.ListNewsHeadlinesWithSource',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.order/order/tradehistory?TradingAccountId=400290710&MaxResults=20', 'Latency CIAPI.ListTradeHistory',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.order/newtradeorder', 'Latency CIAPI.Trade',logdata$key, fixed = TRUE)
```

```{r groupSessionByNodes, echo=FALSE}
nodes <- logdata[logdata$"key" %in% c("ClientIP"), ]

#temp bugfix - this session doesn't seem to report a ClientIP
nodes[2,] <- c("39d948e7-5f2c-4b24-995e-94f1f6c3eab6", "2012-09-03 13:45:42.5018590", "ClientIP", "AWS-EU-WEST-1B-79.125.25.36")

nodes$nodeName = nodes$value
nodes$nodeName <- sub('46.137.47.103', 'AWS-EU-WEST-1B-79.125.25.36',nodes$nodeName, fixed = TRUE)

nodes <- subset(nodes, select=c(-timestamp,-key,-value))
```


Latency between different services
-----------------------------------
The following graph compares the latency of different services for the same node:
```{r service_latency_plot, fig.width=10, fig.height = 7, tidy=FALSE, warning=FALSE}
rpc2 <- logdata[logdata$"key" %in% c("Latency CIAPI.LogIn"
                                    ,"Latency CIAPI.LogOut"
                                    ,"Latency CIAPI.ListSpreadMarkets"
                                    ,"Latency CIAPI.GetClientAndTradingAccount"     
                                    ,"Latency CIAPI.GetMarketInformation"
                                    ,"Latency CIAPI.GetPriceBars"
                                    ,"Latency CIAPI.ListOpenPositions"
                                    ,"Latency CIAPI.ListNewsHeadlinesWithSource"
                                    ,"Latency CIAPI.ListTradeHistory"
                                    ,"Latency CIAPI.Trade" ), ]

rpc2$datetime <- strptime(rpc2$timestamp, "%Y-%m-%d %H:%M:%S")
rpc2$key <- sub('Latency CIAPI.', '',rpc2$key)
rpc2 <- join(rpc2, nodes, by = "session", match = "first")
rpc2 <- rpc2[rpc2$nodeName %in% c("AWS-EU-WEST-1B-79.125.25.36"),]

d <- ggplot(rpc2, aes(x=datetime, y=as.double(value)))
d <- d + ylab("Latency in seconds") + xlab("Measurement time (UTC)")
d <- d + scale_y_log10(breaks=c(0.1,0.3,0.6), limits=c(0.05, 0.7))
d <- d + geom_hex()
d <- d + stat_quantile( quantiles = c(0.5, 0.98) ) 
d <- d + geom_rug(aes(x=NULL, y=as.double(value)), col=rgb(.5,0,0, alpha=.05))
d <- d + scale_fill_gradient(low="grey", high="red") + theme_bw()
d <- d + facet_grid(key ~ nodeName)
d <- d + opts(strip.text.y = theme_text( angle=0))
print(d)
```

Latencies for different services are pretty similar, with the median being around 100ms and the 98th percentile being sub 300ms.

Its noticable that those services which transfer more data - ListSpreadMarkets, ListTradeHistory - are 3 times slower that those that transfer very little data - Login, Trade, etc

Selective latencies in depth
-----------------------------------
The following graph compares:

1. GetClientAndTradingAccount - A "readonly" service query 
1. ListTradeHistory - A complex "readonly" query
1. Login - A simple "change server state" query
1. Trade - A complex "change server state" query

```{r service_latency_plot_in_depth, fig.width=10, fig.height = 7, tidy=FALSE, warning=FALSE}
rpc3 <- logdata[logdata$"key" %in% c("Latency CIAPI.LogIn"
                                    ,"Latency CIAPI.GetClientAndTradingAccount"   
                                    ,"Latency CIAPI.Trade"
                                    ,"Latency CIAPI.ListTradeHistory"), ]

rpc3$datetime <- strptime(rpc3$timestamp, "%Y-%m-%d %H:%M:%S")
rpc3$key <- sub('Latency CIAPI.', '',rpc3$key)
rpc3 <- join(rpc3, nodes, by = "session", match = "first")
rpc3 <- rpc3[rpc3$nodeName %in% c("AWS-EU-WEST-1B-79.125.25.36"),]

d <- ggplot(rpc3, aes(x=datetime, y=as.double(value)))
d <- d + ylab("Latency in seconds") + xlab("Measurement time (UTC)")
d <- d + scale_y_log10() 
d <- d + geom_hex()
d <- d + stat_quantile( quantiles = c(0.5, 0.98) ) 
d <- d + geom_rug(aes(x=NULL, y=as.double(value)), col=rgb(.5,0,0, alpha=.05))
d <- d + scale_fill_gradient(low="grey", high="red") + theme_bw()
d <- d + facet_grid(key ~ nodeName, scales="free_y")
d <- d + opts(strip.text.y = theme_text( angle=0))
print(d)
```

Since the last report a new release of the TradingAPI webserver component has been deployed, and as in the PPE environment we see a dramatic decrease in "low data" services like GetClientTradingAccount, Trade and Login median latency - from around 300ms to sub 100ms.

98% of Trade, GetClientTradingAccount and Login requests where processed within 300ms.

Something unusual happened to the ListTradeHistory latency on 6th and again on the 8th.  At a guess, the amount of data transfered was probably dramatically reduced, perhaps due to some downtime on the backend service supplying the data.

Finally, we still see quite a few outliers for the Trade and Login services, with some requests taking up to 10 seconds to process. 


