```{r init, echo=FALSE}
library("ggplot2")
library("RCurl")
library("plyr")
library("scales")
readRenviron("~/.Renviron") # Make sure you have a APPMETRICS_CREDENTIALS=username:password entry
metrics_credentials <- Sys.getenv(c("APPMETRICS_CREDENTIALS"))
```

```{r fetchData, echo=FALSE}
application <- "CIAPILatencyCollector.AllServiceMonitor.BuiltIn" #will switch to CIAPILatencyCollector once https://github.com/fandrei/AppMetrics/issues/101 has been resolved
startTime <- "2012-09-17 13:00:00"
endTime <- "2012-09-24 23:59:59"
data_url <- URLencode(paste("http://metrics.cityindex.com/GetRecords.ashx?Application=",application,"&StartTime=",startTime,'&EndTime=',endTime, sep = ''))

webpage <- getURL(data_url,userpwd=metrics_credentials, httpauth = 1L)
logdata <- read.table(tc <- textConnection(webpage), header=F, sep="\t", fill=TRUE, as.is=c(1,4)); 
close(tc)
colnames(logdata)=c('session','timestamp','key','value')
```

```{r convert_to_CIAPILatencyCollector_names, echo=FALSE}
# Temporary measure to convert CIAPILatencyCollector.AllServiceMonitor.BuiltIn names to CIAPILatencyCollector names.  Will not be needed once https://github.com/fandrei/AppMetrics/issues/101 has been resolved
logdata$key <- sub('Latency https://ciapi.cityindex.com/TradingApi/', 'Latency CIAPI.',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.session/deleteSession', 'Latency CIAPI.LogOut',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.session', 'Latency CIAPI.LogIn',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.spread/markets?MarketName=&MarketCode=&ClientAccountId=400194351&MaxResults=100&UseMobileShortName=False', 'Latency CIAPI.ListSpreadMarkets',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.useraccount/UserAccount/ClientAndTradingAccount', 'Latency CIAPI.GetClientAndTradingAccount',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.market/400616150/information', 'Latency CIAPI.GetMarketInformation',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.market/400616150/barhistory?interval=MINUTE&span=1&PriceBars=20', 'Latency CIAPI.GetPriceBars',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.order/order/openpositions?TradingAccountId=400290710', 'Latency CIAPI.ListOpenPositions',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.news/dj/UK?MaxResults=10', 'Latency CIAPI.ListNewsHeadlinesWithSource',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.order/order/tradehistory?TradingAccountId=400290710&MaxResults=20', 'Latency CIAPI.ListTradeHistory',logdata$key, fixed = TRUE)
logdata$key <- sub('Latency CIAPI.order/newtradeorder', 'Latency CIAPI.Trade',logdata$key, fixed = TRUE)
```

```{r groupSessionByNodes, echo=FALSE}
nodes <- logdata[logdata$"key" %in% c("ClientIP"), ]

nodes$nodeName = nodes$value
nodes$nodeName <- sub('46.137.47.103', 'AWS-EU-WEST-1B-79.125.25.36', nodes$nodeName, fixed = TRUE)

nodes <- subset(nodes, select=c(-timestamp,-key,-value))
```

Latency between different services
-----------------------------------
The following graph compares the latency of different services for the same node:
```{r service_latency_plot, fig.width=10, fig.height = 7, tidy=FALSE, warning=FALSE, echo=FALSE}
rpc2 <- logdata[logdata$"key" %in% c("Latency CIAPI.LogIn"
                                    ,"Latency CIAPI.LogOut"
                                    ,"Latency CIAPI.ListSpreadMarkets"
                                    ,"Latency CIAPI.GetClientAndTradingAccount"     
                                    ,"Latency CIAPI.GetMarketInformation"
                                    ,"Latency CIAPI.GetPriceBars"
                                    ,"Latency CIAPI.ListOpenPositions"
                                    ,"Latency CIAPI.ListNewsHeadlinesWithSource"
                                    ,"Latency CIAPI.ListTradeHistory"
                                    ,"Latency CIAPI.Trade" ), ]

rpc2$datetime <- strptime(rpc2$timestamp, "%Y-%m-%d %H:%M:%S")
rpc2$key <- sub('Latency CIAPI.', '',rpc2$key)
rpc2 <- join(rpc2, nodes, by = "session", match = "first")
rpc2 <- rpc2[rpc2$nodeName %in% c("AWS-EU-WEST-1B-79.125.25.36"),]

d <- ggplot(rpc2, aes(x=datetime, y=as.double(value)))
d <- d + ylab("Latency in seconds") + xlab("Measurement time (UTC)")
d <- d + scale_y_log10(breaks=c(0.1,0.3,0.6), limits=c(0.05, 0.7))
d <- d + geom_hex()
d <- d + stat_quantile( quantiles = c(0.5, 0.98) ) 
d <- d + geom_rug(aes(x=NULL, y=as.double(value)), col=rgb(.5,0,0, alpha=.05))
d <- d + scale_fill_gradient(low="grey", high="red") + theme_bw()
d <- d + facet_grid(key ~ nodeName)
d <- d + opts(strip.text.y = theme_text( angle=0))
print(d)
```
Some of the services had sudden latency "step changes" during the week.

ListSpreadMarkets and ListNewsHeadlinesWithSource
-----------------------------------
The following graph compares the services that experienced "step changes" during the week.

*NB:*  Note that this graph has a continuous scaled y axis, compared with the log_10 scaling of the first graph.

```{r service_latency_plot_in_depth, fig.width=10, fig.height = 7, tidy=FALSE, warning=FALSE, echo=FALSE}
rpc3 <- logdata[logdata$"key" %in% c("Latency CIAPI.ListNewsHeadlinesWithSource"
                                    ,"Latency CIAPI.ListSpreadMarkets"), ]

rpc3$datetime <- strptime(rpc3$timestamp, "%Y-%m-%d %H:%M:%S")
rpc3$key <- sub('Latency CIAPI.', '',rpc3$key)
rpc3 <- join(rpc3, nodes, by = "session", match = "first")
rpc3 <- rpc3[rpc3$nodeName %in% c("AWS-EU-WEST-1B-79.125.25.36"),]

d <- ggplot(rpc3, aes(x=datetime, y=as.double(value)))
d <- d + ylab("Latency in seconds") + xlab("Measurement time (UTC)")
d <- d + scale_y_continuous(limits=c(0.05, 0.5)) 
d <- d + geom_hex()
d <- d + stat_quantile( quantiles = c(0.5, 0.98) ) 
d <- d + geom_rug(aes(x=NULL, y=as.double(value)), col=rgb(.5,0,0, alpha=.05))
d <- d + scale_fill_gradient(low="grey", high="red") + theme_bw()
d <- d + facet_grid(key ~ nodeName, scales="free_y")
d <- d + opts(strip.text.y = theme_text( angle=0))
print(d)
```

ListSpreadMarkets exhibited large & sudden improvement in performance on Wed 19th Sept that disappeared just as quickly as it arose on Sun Sep 21st.  The only other service that exhibited the same pattern was the ListNewsHeadlinesWithSource service, although the improvements there were not as dramatic.

ListTradeHistory, Login and Trade
-----------------------------------
The following graph compares the services that experienced "step changes" during the week:

*NB:*  Note that this graph has a continuous scaled y axis, compared with the log_10 scaling of the first graph.

```{r service_latency_plot_in_depth2, fig.width=10, fig.height = 7, tidy=FALSE, warning=FALSE, echo=FALSE}
rpc3 <- logdata[logdata$"key" %in% c("Latency CIAPI.LogIn"
                                    ,"Latency CIAPI.Trade"      
                                    ,"Latency CIAPI.ListTradeHistory"), ]

rpc3$datetime <- strptime(rpc3$timestamp, "%Y-%m-%d %H:%M:%S")
rpc3$key <- sub('Latency CIAPI.', '',rpc3$key)
rpc3 <- join(rpc3, nodes, by = "session", match = "first")
rpc3 <- rpc3[rpc3$nodeName %in% c("AWS-EU-WEST-1B-79.125.25.36"),]

d <- ggplot(rpc3, aes(x=datetime, y=as.double(value)))
d <- d + ylab("Latency in seconds") + xlab("Measurement time (UTC)")
d <- d + scale_y_continuous(limits=c(0.05, 0.5)) 
d <- d + geom_hex()
d <- d + stat_quantile( quantiles = c(0.5, 0.98) ) 
d <- d + geom_rug(aes(x=NULL, y=as.double(value)), col=rgb(.5,0,0, alpha=.05))
d <- d + scale_fill_gradient(low="grey", high="red") + theme_bw()
d <- d + facet_grid(key ~ nodeName, scales="free_y")
d <- d + opts(strip.text.y = theme_text( angle=0))
print(d)
```

ListTradeHistory, Login and Trade all seemed to experience a performance degredation during the same period between Thurs 20 Sept and Sun Sept 23.




